---
title: "CR and SB sims results"
author: "Eleanor Hayes-Larson"
date: "2/23/2020"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.align = "center", fig.width = 7)

library(here)
library(knitr)
library(RColorBrewer)
library(wesanderson)
library(tidyverse)
library(ggplot2)

#load results of simulation runs
load(here("Output","AllSims_CRSB.Rdata"))
results<-data.frame(t(data.frame(Allsims_CRSB)))

#convert to long format for plotting
results.long<-gather(results,key=label, value="IRR",IRR.6575, IRR.7585,IRR.8595, IRR.95105)
results.long$label[results.long$label=="IRR.6575"]<-70
results.long$label[results.long$label=="IRR.7585"]<-80
results.long$label[results.long$label=="IRR.8595"]<-90
results.long$label[results.long$label=="IRR.95105"]<-100
```

## Model with only competing risk of death

### Descriptive results

This section includes some descriptive data that is in the manuscript results. The following plot shows the proportion of the cohort in each of 5 states in the competing risks only scenario for all types of cancer. 

```{r CRonlycohort}

#Saving dataset of only competing risk of death only scenario for all cancers

    CRonly_base<-data.frame(results[results$S1.dem.rateratio==1 & 
                                    results$S1.mort.rateratio==1 & 
                                    results$Sprev==0 & 
                                    results$cancertype=="all","outdata"])
    colnames(CRonly_base)<-substr(colnames(CRonly_base),6,10000)  #fixing col names
    CRonly_base<-CRonly_base[CRonly_base$time!=10000,] #drop unneeded time=10000 yrs
    CRonly_base$C0D0<-CRonly_base$C0D0S0+CRonly_base$C0D0S1
    CRonly_base$C0D1<-CRonly_base$C0D1S0+CRonly_base$C0D1S1
    CRonly_base$C1D0<-CRonly_base$C1D0S0+CRonly_base$C1D0S1
    CRonly_base$C1D1<-CRonly_base$C1D1S0+CRonly_base$C1D1S1
    test<-c("time","C0D0", "C0D1", "C1D0", "C1D1", "DEAD")
    CRonly_base<-CRonly_base[,test]
    to.plot<-gather(CRonly_base, "state","number",-time)
    to.plot<-to.plot[order(factor(to.plot$state, levels=c("C0D0","C1D0","C0D1","C1D1","DEAD"))),]
                     
    colorset<-c(brewer.pal(8,"Paired")[c(1,7,2,8)],brewer.pal(8,"Dark2")[8])

#Plots of cohort transitions
#Next 5 plots are a build for a presentation. Only last "cohort_buildfinal" is in paper.
    Cohort_build1<-ggplot(to.plot[to.plot$state=="C0D0",],
                          aes(time,number,
                              group=factor(state, levels=c("C0D0","C1D0","C0D1","C1D1","DEAD")),
                              color=factor(state, levels=c("C0D0","C1D0","C0D1","C1D1","DEAD"))))+
                    geom_line(size=2) +
                    ylab("Proportion of cohort in each state")+
                    theme_bw()+
                    scale_color_manual(name=NULL,values=colorset, labels=c("No cancer, no dementia"))+
                    xlab("Time (years since age 65)")+
                    theme(legend.position = c(0.8,0.5),axis.text.x = element_text(size=16), 
        axis.text.y = element_text(size=16), 
        axis.title.x = element_text(size=16, face="bold"), 
        axis.title.y = element_text(size=16, face="bold"))
    
    ggsave(here("Output","CR and SB Figures", "Cohort_build1.png"), 
           plot = Cohort_build1, device = NULL, path = NULL, scale = 1, 
           width = 7.5, height = 5, units = "in", dpi = 300, limitsize = TRUE)
    
    Cohort_build2<-ggplot(to.plot[to.plot$state=="C0D0"|to.plot$state=="C1D0",],
                          aes(time,number,group=factor(state, levels=c("C0D0","C1D0","C0D1","C1D1","DEAD")),
                              color=factor(state, levels=c("C0D0","C1D0","C0D1","C1D1","DEAD"))))+
                    geom_line(size=2) + 
                    ylab("Proportion of cohort in each state")+theme_bw()+
                    scale_color_manual(name=NULL,values=colorset, 
                                       labels=c("No cancer, no dementia", "Cancer, no dementia"))+
                    xlab("Time (years since age 65)")+theme(legend.position = c(0.8,0.5),axis.text.x = element_text(size=16), 
        axis.text.y = element_text(size=16), 
        axis.title.x = element_text(size=16, face="bold"), 
        axis.title.y = element_text(size=16, face="bold"))
    
    ggsave(here("Output","CR and SB Figures", "Cohort_build2.png"), 
           plot = Cohort_build2, device = NULL, path = NULL, scale = 1, 
           width = 7.5, height = 5, units = "in", dpi = 300, limitsize = TRUE)
    
    Cohort_build3<-ggplot(to.plot[to.plot$state=="C0D0"|to.plot$state=="C1D0"|to.plot$state=="C0D1",],
                          aes(time,number,group=factor(state, levels=c("C0D0","C1D0","C0D1","C1D1","DEAD")),
                              color=factor(state, levels=c("C0D0","C1D0","C0D1","C1D1","DEAD"))))+
                          geom_line(size=2) + 
                          ylab("Proportion of cohort in each state")+theme_bw()+
                          scale_color_manual(name=NULL,values=colorset, 
                                             labels=c("No cancer, no dementia","Cancer, no dementia","No cancer, dementia"))+
                          xlab("Time (years since age 65)")+theme(legend.position = c(0.8,0.5),axis.text.x = element_text(size=16), 
        axis.text.y = element_text(size=16), 
        axis.title.x = element_text(size=16, face="bold"), 
        axis.title.y = element_text(size=16, face="bold"))
    
    ggsave(here("Output","CR and SB Figures", "Cohort_build3.png"), 
           plot = Cohort_build3, device = NULL, path = NULL, scale = 1, 
           width = 7.5, height = 5, units = "in", dpi = 300, limitsize = TRUE)
    
    Cohort_build4<-ggplot(to.plot[to.plot$state=="C0D0"|to.plot$state=="C1D0"|to.plot$state=="C0D1"|to.plot$state=="C1D1",],
                          aes(time,number,group=factor(state, levels=c("C0D0","C1D0","C0D1","C1D1","DEAD")),
                              color=factor(state, levels=c("C0D0","C1D0","C0D1","C1D1","DEAD"))))+
                          geom_line(size=2) + ylab("Proportion of cohort in each state")+
                          theme_bw()+
                          scale_color_manual(name=NULL,values=colorset, 
                                             labels=c("No cancer, no dementia", "Cancer, no dementia", 
                                                      "No cancer, dementia", "Cancer, dementia"))+
                          xlab("Time (years since age 65)")+theme(legend.position = c(0.8,0.5),axis.text.x = element_text(size=16), 
        axis.text.y = element_text(size=16), 
        axis.title.x = element_text(size=16, face="bold"), 
        axis.title.y = element_text(size=16, face="bold"))
    
    ggsave(here("Output","CR and SB Figures", "Cohort_build4.png"), 
           plot = Cohort_build4, device = NULL, path = NULL, scale = 1, 
           width = 7.5, height = 5, units = "in", dpi = 300, limitsize = TRUE)
    
    
    Cohort_buildfinal<-ggplot(to.plot,aes(time,number,
                                          group=factor(state, levels=c("C0D0","C1D0","C0D1","C1D1","DEAD")),
                                          color=factor(state, levels=c("C0D0","C1D0","C0D1","C1D1","DEAD"))))+
                        geom_line(size=2) + ylab("Proportion of cohort in each state")+theme_bw()+
                        scale_color_manual(name=NULL,values=colorset, 
                                           labels=c("No cancer, no dementia", "Cancer, no dementia",
                                                    "No cancer, dementia", "Cancer, dementia", "Dead"))+
                        xlab("Time (years since age 65)")+theme(legend.position = c(0.8,0.5),
                                                   axis.text.x = element_text(size=16), 
        axis.text.y = element_text(size=16), 
        axis.title.x = element_text(size=16, face="bold"), 
        axis.title.y = element_text(size=16, face="bold"))
    
    ggsave(here("Output","CR and SB Figures", "Cohort_buildfinal.png"), 
           plot = Cohort_buildfinal, device = NULL, path = NULL, scale = 1, 
           width = 7.5, height = 5, units = "in", dpi = 300, limitsize = TRUE)
    
    Cohort_buildfinal

```



The median survival time in this cohort is between `r round(last(CRonly_base$time[CRonly_base$DEAD<0.5]),2)` and `r round(first(CRonly_base$time[CRonly_base$DEAD>0.5]),2)` years.

```{r}
#Calculate dementia incidence rates in CR only simulation
out.data<-data.frame(results[results$S1.dem.rateratio==1 & 
                                    results$S1.mort.rateratio==1 & 
                                    results$Sprev==0 & 
                                    results$cancertype=="all","outdata"])
    colnames(out.data)<-substr(colnames(out.data),6,10000)  #fixing col names

#Sorry for the cloning and growing, but this code is copy and pasted from 
  # the calibration plot function.R script. 
  # Didn't think I'd need these results but they are for 1 line in the paper!

dem_inc_mod<-rep(NA,6)

for (i in seq(from=5, to=30, by=5)){
  if (i<30){
    ncases.dem.interval<-out.data$DEMENTIA[out.data$time==i]-out.data$DEMENTIA[out.data$time==(i-5)]
    
    ncases.dem.months<-rep(NA,60)
    ndeathsnodem.months<-rep(NA,60)
    PT.dem.death<-0
     
    #Add up person time in each month
    for (j in seq(from=1/12, to=5, by=1/12)){
      ncases.dem.months[j*12] <- out.data$DEMENTIA[round(out.data$time,2)==round(i-(5-j),2)]-out.data$DEMENTIA[round(out.data$time,2)==round((i-(5-j)-1/12),2)]
      ndeathsnodem.months[j*12] <- out.data$DEADC0D0S0[round(out.data$time,2)==round(i-(5-j),2)]-out.data$DEADC0D0S0[round(out.data$time,2)==round((i-(5-j)-1/12),2)] +
                                out.data$DEADC1D0S0[round(out.data$time,2)==round(i-(5-j),2)]-out.data$DEADC1D0S0[round(out.data$time,2)==round((i-(5-j)-1/12),2)] +
                                out.data$DEADC0D0S1[round(out.data$time,2)==round(i-(5-j),2)]-out.data$DEADC0D0S1[round(out.data$time,2)==round((i-(5-j)-1/12),2)] +
                                out.data$DEADC1D0S1[round(out.data$time,2)==round(i-(5-j),2)]-out.data$DEADC1D0S1[round(out.data$time,2)==round((i-(5-j)-1/12),2)]
      PT.dem.death<-PT.dem.death+((j-(0.5/12))*(ndeathsnodem.months[j*12]+ncases.dem.months[j*12]))
    }
    
    #Rate is cases/persontime 
    dem_inc_mod[i/5]<-ncases.dem.interval/(5*(out.data$C0D0S0[round(out.data$time,2)==round(i,2)] +
                                            out.data$C1D0S0[round(out.data$time,2)==round(i,2)] +
                                            out.data$C0D0S1[round(out.data$time,2)==round(i,2)] +
                                            out.data$C1D0S1[round(out.data$time,2)==round(i,2)] ) +
                                         PT.dem.death)
  }
  else {
    ncases.dem.interval<-out.data$DEMENTIA[out.data$time==(i+10)]-out.data$DEMENTIA[out.data$time==(i-5)]
    ncases.dem.months<-rep(NA,15*12)
    ndeathsnodem.months<-rep(NA,15*12)
    PT.dem.death<-0
    
    #Add up person time in each year
    for (j in seq(from=1/12, to=15, by=1/12)){
      ncases.dem.months[j*12]<-out.data$DEMENTIA[round(out.data$time,2)==round((i+10)-(15-j),2)]-out.data$DEMENTIA[round(out.data$time,2)==round(((i+10)-(15-j)-1/12),2)]
      ndeathsnodem.months[j*12]<-  out.data$DEADC0D0S0[round(out.data$time,2)==round((i+10)-(15-j),2)] - out.data$DEADC0D0S0[round(out.data$time,2)==round(((i+10)-(15-j)-1/12),2)] +
                                   out.data$DEADC1D0S0[round(out.data$time,2)==round((i+10)-(15-j),2)] - out.data$DEADC1D0S0[round(out.data$time,2)==round(((i+10)-(15-j)-1/12),2)] + 
                                   out.data$DEADC0D0S1[round(out.data$time,2)==round((i+10)-(15-j),2)] - out.data$DEADC0D0S1[round(out.data$time,2)==round(((i+10)-(15-j)-1/12),2)] +
                                   out.data$DEADC1D0S1[round(out.data$time,2)==round((i+10)-(15-j),2)] - out.data$DEADC1D0S1[round(out.data$time,2)==round(((i+10)-(15-j)-1/12),2)] 
                              
      PT.dem.death<-PT.dem.death+((j-1/24)*(ndeathsnodem.months[j*12]+ncases.dem.months[j*12]))
    }
    
    #Rate is cases/persontime 
    dem_inc_mod[i/5]<-ncases.dem.interval/(15*(out.data$C0D0S0[out.data$time==(i+10)] +
                                               out.data$C1D0S0[out.data$time==(i+10)] +
                                               out.data$C0D0S1[out.data$time==(i+10)] +
                                               out.data$C1D0S1[out.data$time==(i+10)] ) +
                                           PT.dem.death)    
  }}


```


The dementia incidence rate in this cohort `r dem_inc_mod[1]*1000` per 1,000 person years for ages 65-69, and  `r dem_inc_mod[6]*1000` per 1,000 person years for ages 95+.  


### Measures of association

The following results show the cumulative incidence ratio (CIR) and age-specific incidence rate ratios for each cancer type for the scenarios with only competing risks.

#### Cumulative incidence ratio, competing risk of death only

```{r CRonlyresults_CIR}
#-----------------------------------------------
#CIR results for CR only scenario
#-----------------------------------------------

    #Plot of CIRs
    CRonly_baseCIR<-data.frame(lapply(data.frame(results[results$S1.dem.rateratio==1 & results$S1.mort.rateratio==1 & results$Sprev==0,c("cancertype", "lifetimeRR")]),unlist))
    
    colorset2<-c("gray","seagreen3","mediumorchid3","steelblue")
    
    
    CIRplot<-ggplot(data=CRonly_baseCIR, 
                    aes(x=factor(cancertype, levels=c("all", "lung", "breast", "prostate")), 
                        y=lifetimeRR, ymin=lifetimeRR, ymax=lifetimeRR), color=as.factor(cancertype))+ylim(0,1.25)+
      geom_pointrange(size=2, shape=15, color=colorset2) +
      xlab("Cancer type")+ ylab("Observed CIR for dementia \n(cancer vs. no cancer)")+ 
      scale_color_manual(values=colorset2)+ scale_x_discrete(labels=c("all"="All", "lung"="Lung", "breast"="Breast", "prostate"="Prostate"))+
      theme_bw()+
      geom_hline(yintercept=1, colour="black", lwd=1) +
      theme(axis.text.x = element_text(size=18), 
            axis.text.y = element_text(size=18), 
            axis.title.x = element_text(size=18, face="bold"), 
            axis.title.y = element_text(size=18, face="bold"), 
            legend.position = "bottom"
      )
    CIRplot
    
    
    ggsave(here("Output","CR and SB Figures","CRonly_CIR.png"), plot = CIRplot, device = NULL, path = NULL, scale = 1, width = 7.5, height = 5, units = "in", dpi = 300, limitsize = TRUE)
    
    #Output values
    cat(print(knitr::kable(CRonly_baseCIR)),"/n")
```



#### Incidence rate ratios, competing risk of death only

```{r CRonlyresults_IRR}
#-----------------------------------------------
#Now look at IRRs for CR only scenario
#-----------------------------------------------
  CRonly_baseIRRs<-data.frame(lapply(results.long[results.long$S1.dem.rateratio==1 & results.long$S1.mort.rateratio==1 & results.long$Sprev==0, c("cancertype", "IRR", "label")], unlist))
  
  CR.IRRplot<-ggplot(data=CRonly_baseIRRs)+
    geom_pointrange(aes(x=factor(label, levels=c("70", "80","90","100")), y=IRR, ymin=IRR, ymax=IRR, group=as.factor(cancertype), color=as.factor(cancertype)), position=position_dodge(width=0.2), size=2, shape=15)+ylim(0.8,1.0001)+
    xlab("Age range")+ ylab("Observed IRR for dementia \n(cancer vs. no cancer)")+
    scale_color_manual(name="", labels=c("All cancers", "Lung", "Breast", "Prostate"), values=colorset2)+scale_x_discrete(labels=c("70"="65-74", "80"="75-84", "90"="85-94", "100"="95-104"))+
    theme_bw()+
    geom_hline(yintercept=1, colour="black", lwd=1) +
    theme(axis.text.x = element_text(size=18), 
        axis.text.y = element_text(size=18), 
        axis.title.x = element_text(size=18, face="bold"), 
        axis.title.y = element_text(size=18, face="bold"), 
        legend.position = c(0.8,.3),
        legend.text = element_text(size=16)
    )
  CR.IRRplot
  
  ggsave(here("Output","CR and SB Figures","CRonly_IRR.png"), plot = CR.IRRplot, device = NULL, path = NULL, scale = 1, width = 7.5, height = 5, units = "in", dpi = 300, limitsize = TRUE)
  
  
  #Output values
  CRonly_baseIRRs_table<-
    data.frame(lapply(data.frame(results[results$S1.dem.rateratio==1 & results$S1.mort.rateratio==1 & results$Sprev==0,
                                         c("cancertype", "IRR.6575", "IRR.7585", "IRR.8595", "IRR.95105", "IRR.overall")]),unlist))
  cat(print(knitr::kable(CRonly_baseIRRs_table)), "/n")


```



## Model with selective survival

The following plots show the CIR and IRRs and the prevalence of U for each cancer type after selective survival is introduced. They are shown for the base case model, where the prevalence of U is 30%, and U reduces both cancer mortality and dementia incidence by 30% (IRRs = 0.7). 



#### Cumulative incidence ratio, with selective survival (base case)


```{r baseCRSB_CIR}
#------------------------------------------
# CIR results for selective survival model base case
#------------------------------------------


colorset3<-c("gray","mediumorchid3","seagreen3","steelblue")

baseCRSB<-results.long[results.long$Sprev==0.3 & results.long$S1.dem.rateratio==0.7 & results.long$S1.mort.rateratio==0.7,]

plot.CIR.baseCRSB<-ggplot(data=baseCRSB[1:4,], aes(x=factor(cancertype, levels=c("all", "lung", "breast", "prostate")), y=unlist(lifetimeRR), ymin=unlist(lifetimeRR), ymax=unlist(lifetimeRR)), color=as.factor(cancertype))+ylim(0,1.25)+
  geom_pointrange(size=2, shape=17, color=colorset2) +
  xlab("Cancer type")+ ylab("Observed CIR for dementia \n(cancer vs. no cancer)")+ 
  scale_color_manual(values=colorset2)+ scale_x_discrete(labels=c("all"="All", "lung"="Lung", "breast"="Breast", "prostate"="Prostate"))+
  theme_bw()+
  geom_hline(yintercept=1, colour="black", lwd=1) +
  theme(axis.text.x = element_text(size=18), 
        axis.text.y = element_text(size=18), 
        axis.title.x = element_text(size=18, face="bold"), 
        axis.title.y = element_text(size=18, face="bold"), 
        legend.position = "bottom",
        legend.text = element_text(size=10)
  )
plot.CIR.baseCRSB

ggsave(here("Output", "CR and SB Figures","CRSB_CIR.png"), plot = plot.CIR.baseCRSB, device = NULL, path = NULL, scale = 1, width = 7.5, height = 5, units = "in", dpi = 300, limitsize = TRUE)


    cat(print(knitr::kable(baseCRSB[1:4,c("cancertype", "lifetimeRR")])),"/n")

```




#### Incidence rate ratios, with selective survival (base case)


```{r baseCRSB_IRR}
#------------------------------------------
# IRR results for selective survival model base case
#------------------------------------------

plot.IRR.baseCRSB<-ggplot(baseCRSB, aes(x=as.numeric(unlist(label)), y=unlist(IRR), group=factor(unlist(cancertype)), color=factor(unlist(cancertype)))) + geom_point(size=7, shape=17) + geom_line(size=1,linetype="longdash")+scale_color_manual(values = colorset3, labels=c("all"="All", "lung"="Lung", "breast"="Breast", "prostate"="Prostate"))+ylim(0.8,1.0001)+
  ylab("Observed IRR for dementia \n(cancer vs. no cancer)") + xlab("Age range")+ labs(color = NULL) +
  scale_x_continuous(name="Age range", breaks=c(70,80,90,100), labels=c("65-74", "75-84","85-94","95-104"))+
    geom_hline(yintercept=1, colour="black", lwd=1) +
  theme_bw()+
  theme(
    legend.position= c(0.8,.3), 
    axis.text.x = element_text(size=18), 
    axis.text.y = element_text(size=18), 
    axis.title.x = element_text(size=18, face="bold"), 
    axis.title.y = element_text(size=18, face="bold"), 
    plot.title = element_text(hjust = 0.5),
    panel.grid.minor = element_blank(),
    panel.grid.minor.y = element_blank(),
    legend.text = element_text(size=16))
plot.IRR.baseCRSB

ggsave(here("Output", "CR and SB Figures","CRSB_IRR.png"), plot = plot.IRR.baseCRSB, device = NULL, path = NULL, scale = 1, width = 7.5, height = 5, units = "in", dpi = 300, limitsize = TRUE)


 #Output values
  baseCRSB_table<-
    data.frame(lapply(data.frame(results[results$S1.dem.rateratio==.7 & results$S1.mort.rateratio==.7 & results$Sprev==0.5,
                                         c("cancertype", "IRR.6575", "IRR.7585", "IRR.8595", "IRR.95105", "IRR.overall")]),unlist))
  cat(print(knitr::kable(baseCRSB_table)), "/n")


```



## Prevalence of U over time

The following plot shows the prevalence of U over time for selected models. 


#### Base case selective survival model: U dem IRR=0.7, U mort IRR=0.7, U prev=0.3.


```{r Uprev1, warning=FALSE}

#------------------------------------------
# Plot results for prevalence of U in CR and SB scenario
#------------------------------------------
Uprevs.CRSbbase<-data.frame(results[results$S1.dem.rateratio==0.7 & results$S1.mort.rateratio==0.7 & results$Sprev==0.3 & 
                             results$cancertype=="all","outdata"])
colnames(Uprevs.CRSbbase)<-substr(colnames(Uprevs.CRSbbase),5,10000)
Uprevs.CRSbbase<-Uprevs.CRSbbase[Uprevs.CRSbbase$time!=10000,c("time", "C1D0S1", "C0D0S1", "C1D0S0", "C0D0S0")]
Uprevs.CRSbbase$Sprevalive.demfree.C<-Uprevs.CRSbbase$C1D0S1/(Uprevs.CRSbbase$C1D0S0+Uprevs.CRSbbase$C1D0S1)
Uprevs.CRSbbase$Sprevalive.demfree.noC<-Uprevs.CRSbbase$C0D0S1/(Uprevs.CRSbbase$C0D0S1+Uprevs.CRSbbase$C0D0S0)

to.plotU<-gather(Uprevs.CRSbbase,key=cancer,value="Sprevalive.demfree",Sprevalive.demfree.C, Sprevalive.demfree.noC)


CRSB_Uprev<-ggplot(to.plotU, aes(time,Sprevalive.demfree,group=cancer, linetype=cancer))+geom_line(size=1.5)+
  ylab("Prevalence of U in \nthose surviving dementia-free ") + ylim(0,1) +
  xlab("Time (years)")+
  scale_linetype_manual(values=c(1, 6),labels=c("Cancer history", "No cancer history"))+
  theme_bw()+
  theme(legend.title = element_blank(),
        legend.position = c(0.2,0.81),    
        axis.text.x = element_text(size=18), 
        axis.text.y = element_text(size=18), 
        axis.title.x = element_text(size=18, face="bold"), 
        axis.title.y = element_text(size=18, face="bold"),
        legend.text = element_text(size=10)
  )
CRSB_Uprev

ggsave(here("Output", "CR and SB Figures","CRSB_Uprev.png"), plot = CRSB_Uprev, device = NULL, path = NULL, scale = 1, width = 7.5, height = 5, units = "in", dpi = 300, limitsize = TRUE)


print(paste("The prevalence of U among those alive without history of cancer at age 75 years is ",round(Uprevs.CRSbbase$Sprevalive.demfree.noC[Uprevs.CRSbbase$time==10]*100,1),"%.",sep=""))

print(paste("The prevalence of U among those alive without history of cancer at age 95 years is ",round(Uprevs.CRSbbase$Sprevalive.demfree.noC[Uprevs.CRSbbase$time==30]*100,1),"%.",sep=""))

print(paste("The prevalence of U among those alive without history of cancer at age 105 years is ",round(Uprevs.CRSbbase$Sprevalive.demfree.noC[Uprevs.CRSbbase$time==40]*100,1),"%.",sep=""))

print(paste("The prevalence of U among those alive with history of cancer at age 75 years is ",round(Uprevs.CRSbbase$Sprevalive.demfree.C[Uprevs.CRSbbase$time==10]*100,1),"%.",sep=""))

print(paste("The prevalence of U among those alive with history of cancer at age 95 years is ",round(Uprevs.CRSbbase$Sprevalive.demfree.C[Uprevs.CRSbbase$time==30]*100,1),"%.",sep=""))

print(paste("The prevalence of U among those alive with history of cancer at age 105 years is ",round(Uprevs.CRSbbase$Sprevalive.demfree.C[Uprevs.CRSbbase$time==40]*100,1),"%.",sep=""))

```



#### Extreme selective survival model: S dem IRR=0.3, S mort IRR=0.3, S prev=0.5.

```{r Uprev2, warning=FALSE}

#------------------------------------------
# Plot results for prevalence of U in CR and SB scenario
#------------------------------------------
Uprevs.CRSbbase<-data.frame(results[results$S1.dem.rateratio==0.3 & results$S1.mort.rateratio==0.3 & results$Sprev==0.5 & 
                             results$cancertype=="all","outdata"])
colnames(Uprevs.CRSbbase)<-substr(colnames(Uprevs.CRSbbase),5,10000)
Uprevs.CRSbbase<-Uprevs.CRSbbase[Uprevs.CRSbbase$time!=10000,c("time", "C1D0S1", "C0D0S1", "C1D0S0", "C0D0S0")]
Uprevs.CRSbbase$Sprevalive.demfree.C<-Uprevs.CRSbbase$C1D0S1/(Uprevs.CRSbbase$C1D0S0+Uprevs.CRSbbase$C1D0S1)
Uprevs.CRSbbase$Sprevalive.demfree.noC<-Uprevs.CRSbbase$C0D0S1/(Uprevs.CRSbbase$C0D0S1+Uprevs.CRSbbase$C0D0S0)

to.plotU<-gather(Uprevs.CRSbbase,key=cancer,value="Sprevalive.demfree",Sprevalive.demfree.C, Sprevalive.demfree.noC)


CRSB_Uprev2<-ggplot(to.plotU, aes(time,Sprevalive.demfree,group=cancer, linetype=cancer))+geom_line(size=1.5)+
  ylab("Prevalence of U in \nthose surviving dementia-free") + ylim(0,1) +
  xlab("Time (years)")+
  scale_linetype_manual(values=c(1, 6),labels=c("Cancer history", "No cancer history"))+
  theme_bw()+theme(legend.title = element_blank(),legend.position = c(0.2,0.81),    
        axis.text.x = element_text(size=18), 
        axis.text.y = element_text(size=18), 
        axis.title.x = element_text(size=18, face="bold"), 
        axis.title.y = element_text(size=18, face="bold"),
        legend.text = element_text(size=10))
CRSB_Uprev2

ggsave(here("Output", "CR and SB Figures","CRSB_Uprev2.png"), plot = CRSB_Uprev2, device = NULL, path = NULL, scale = 1, width = 7.5, height = 5, units = "in", dpi = 300, limitsize = TRUE)


```

#### Extreme selective survival model: S dem IRR=0.3, S mort IRR=0.3, S prev=0.1.

```{r Uprev3, warning=FALSE}

#------------------------------------------
# Plot results for prevalence of U in CR and SB scenario
#------------------------------------------
Uprevs.CRSbbase<-data.frame(results[results$S1.dem.rateratio==0.3 & results$S1.mort.rateratio==0.3 & results$Sprev==0.1 & 
                             results$cancertype=="all","outdata"])
colnames(Uprevs.CRSbbase)<-substr(colnames(Uprevs.CRSbbase),6,10000)
Uprevs.CRSbbase<-Uprevs.CRSbbase[Uprevs.CRSbbase$time!=10000,c("time", "C1D0S1", "C0D0S1", "C1D0S0", "C0D0S0")]
Uprevs.CRSbbase$Sprevalive.demfree.C<-Uprevs.CRSbbase$C1D0S1/(Uprevs.CRSbbase$C1D0S0+Uprevs.CRSbbase$C1D0S1)
Uprevs.CRSbbase$Sprevalive.demfree.noC<-Uprevs.CRSbbase$C0D0S1/(Uprevs.CRSbbase$C0D0S1+Uprevs.CRSbbase$C0D0S0)

to.plotU<-gather(Uprevs.CRSbbase,key=cancer,value="Sprevalive.demfree",Sprevalive.demfree.C, Sprevalive.demfree.noC)


CRSB_Uprev3<-ggplot(to.plotU, aes(time,Sprevalive.demfree,group=cancer, linetype=cancer))+geom_line(size=1.5)+
  ylab("Prevalence of U in \nthose surviving dementia-free ")+ ylim(0,1) +
  xlab("Time (years)")+
  scale_linetype_manual(values=c(1, 6),labels=c("Cancer history", "No cancer history"))+
  theme_bw()+theme(legend.title = element_blank(),legend.position = c(0.2,0.81),    
        axis.text.x = element_text(size=18), 
        axis.text.y = element_text(size=18), 
        axis.title.x = element_text(size=18, face="bold"), 
        axis.title.y = element_text(size=18, face="bold"),
        legend.text = element_text(size=10))
CRSB_Uprev3

ggsave(here("Output", "CR and SB Figures","CRSB_Uprev3.png"), plot = CRSB_Uprev3, device = NULL, path = NULL, scale = 1, width = 7.5, height = 5, units = "in", dpi = 300, limitsize = TRUE)


```




## Sensitivity analyses
The most bias observed for the all cancers model was an overall IRR of `r min(unlist(results$IRR.overall[results$cancertype=="all"]))`, for the scenario with IRR for U on cancer mortality of `r results$S1.mort.rateratio[results$IRR.overall==min(unlist(results$IRR.overall[results$cancertype=="all"]))]`, IRR for U on dementia incidence of `r results$S1.dem.rateratio [results$IRR.overall==min(unlist(results$IRR.overall[results$cancertype=="all"]))]`, and U prevalence of at baseline `r results$Sprev [results$IRR.overall==min(unlist(results$IRR.overall[results$cancertype=="all"]))]`.


The most bias observed for any cancer  was an overall IRR of `r min(unlist(results$IRR.overall))`, for the scenario for `r results$cancer [results$IRR.overall==min(unlist(results$IRR.overall))]` cancer, IRR for U on cancer mortality of `r results$S1.mort.rateratio [results$IRR.overall==min(unlist(results$IRR.overall))]`, IRR for U on dementia incidence of `r results$S1.dem.rateratio [results$IRR.overall==min(unlist(results$IRR.overall))]`, and U prevalence of at baseline `r results$Sprev [results$IRR.overall==min(unlist(results$IRR.overall))]`.

 
The following plot shows the results of the sensitivity analyses for varying strengths of selective survival for the simulation model for all cancer types. 


```{r, sensplots}

#------------------------------------------------------------------
# Plot sensitivity results for all types of cancer 
#------------------------------------------------------------------

c_all<-c("gray35", "gray45", "gray55", "gray65", "gray75")
c_breast<-c( "mediumorchid4", "darkorchid","mediumorchid3", "mediumorchid2", "mediumorchid1")
c_lung<-c("seagreen","seagreen4", "seagreen3", "seagreen2", "seagreen1")
c_prostate<-c("steelblue4", "steelblue", "steelblue3", "steelblue2", "steelblue1")

sensplots<-function(cantype, colset){
  plot.IRR<-ggplot(results.long[results.long$cancertype==cantype & results.long$Sprev>=0.1,], 
                   aes(x=as.numeric(unlist(label)), y=unlist(IRR), group=unlist(S1.mort.rateratio), color=factor(unlist(S1.mort.rateratio)))) + geom_point(size=2, shape=17) + geom_line(size=1)+ylim(0.4,1.1)+
    facet_grid(unlist(Sprev)~.~unlist(S1.dem.rateratio), labeller=label_value)+scale_color_manual(values = colset)+
    ylab("Observed IRR for dementia \n(cancer vs. no cancer)") + labs(color = paste("Rate ratio for U on ",cantype," cancer mortality")) + ggtitle("Rate ratio for U on dementia incidence")+
      scale_x_continuous(name="Age range", breaks=c(70,80,90,100), labels=c("65-74", "75-84","85-94","95-104"))+
    theme_bw()+
    theme(
      legend.position="bottom", 
      axis.text.x = element_text(size=8), 
      axis.text.y = element_text(size=8.5), 
      axis.title.x = element_text(size=14, face="bold"), 
      axis.title.y = element_text(size=14, face="bold"), 
      plot.title = element_text(hjust = 0.5),
      panel.grid.minor = element_blank(),
      panel.grid.minor.y = element_blank(),
      panel.spacing = unit(1.25, "lines"))
  
  

  ggsave(here("Output","CR and SB Figures",paste("CRSB_sens_",cantype,".png")),
       plot = plot.IRR, device = NULL, path = NULL, scale = 1, width = 7.5, 
       height = 7.5, units = "in", dpi = 600, limitsize = TRUE)
  
  print(plot.IRR)
  
  
  overallplot<-ggplot(results[results$cancertype==cantype & results$Sprev>=0.1,], 
                   aes(x=(unlist(S1.dem.rateratio)), 
                       y=as.numeric(unlist(IRR.overall)), 
                       group=factor(unlist(S1.mort.rateratio)), 
                       color=factor(unlist(S1.mort.rateratio)))) + 
  geom_point(size=2, shape=17) + geom_line(size=1)+ylim(0.8,1.0001)+
    facet_grid(.~unlist(Sprev), labeller=label_value)+
    ylab("Observed overall IRR for dementia \n(cancer vs. no cancer)") + labs(color = paste("IRR for U on", cantype, "cancer mortality")) + scale_color_manual(values=colset)+
      scale_x_continuous(name="IRR for U on dementia incidence", breaks=c(0.3, 0.5, 0.7, 0.9))+
  ggtitle("Prevalence of U in cohort at baseline")+
    theme_bw()+
    theme(
      legend.position="bottom", 
      axis.text.x = element_text(size=10), 
      axis.text.y = element_text(size=16), 
      axis.title.x = element_text(size=11, face="bold"), 
      axis.title.y = element_text(size=11, face="bold"), 
      plot.title = element_text(size=11, face="bold", hjust = 0.5),
      panel.grid.minor = element_blank(),
      panel.grid.minor.y = element_blank(),
      panel.spacing = unit(1, "lines"))

  ggsave(here("Output","CR and SB Figures",paste("CRSB_sens_overall_",cantype,".png")),
       plot = overallplot, device = NULL, path = NULL, scale = 1, width = 7.5, 
       height = 5, units = "in", dpi = 600, limitsize = TRUE)
  
  print(overallplot)
  
}

sensplots("all",c_all)
sensplots("breast",c_breast)
sensplots("lung",c_lung)
sensplots("prostate",c_prostate)


```

